Boutiques: a flexible framework for automated application integration in computing platforms

### 2016-12-05 paper.tex

\todo{Sorina, Tristan}

>>>>

The Virtual Imaging Platform (VIP)~\cite{GLAT-13} is a web portal for medical 
simulation  and image data analysis. VIP allows to make applications 
available as a service, and also to benefit from the resources available 
to the biomed Virtual Organisation (VO) of the European Grid Infrastructure 
\footnote{\url{https://www.egi.eu/}}, supported by approximately 65 computing
sites world-wide offering a total of 130 computing clusters
and 5 PB of storage. The VIP service is currently deployed at the Creatis laboratory
\footnote{\url{https://www.creatis.insa-lyon.fr/site7/en}} and uses the DIRAC 
French service \footnote{\url{https://dirac.france-grilles.fr}} to submit jobs on 
EGI grid and cloud resources.  VIP counts, in December 2016, more than 950 
registered users and a growing number of available applications.

Until recently, applications were integrated in VIP as workflows defined and managed 
with the MOTEUR\cite{GLAT-08} workflow engine. As of today, Boutiques is supported 
through a "Boutiques application importer" tool allowing to automatically import
applications based on their JSON description.

\todo{Sorina, Tristan: develop on the functionalities and current limits of the application importer?}
